Large Linear Multi-output Gaussian Process Learning for Time Series

### 2017-05-30 paper/paper.tex
Remove NIPS references from arxiv paper
got rid of eps files
missing url

\PassOptionsToPackage{numbers, compress}{natbib}
% Camera ready: \usepackage[final]{nips_2017}
\usepackage{nips_2017}

@@

\begin{figure}[!h]
\begin{center}
  \subfigure[]{\includegraphics[width=0.4\columnwidth]{iterations.eps}}
  \subfigure[]{\includegraphics[width=0.4\columnwidth]{running_cutoff.eps}}
\end{center}
\caption{Trace of (a) the number of MVMs that \textsc{minres} must perform to invert $K_{|\bsth}^{-1}\Ty$ and (b) $\mcL, \norm{\nabla\mcL}$ given $\bsth$ at each optimization iteration for a GP applied to the dataset in Sec.~\ref{fx2007-results}. In (b), in green, we have 20\% of the rolling maximum $\infty$-norm of previous gradients.
}
\label{fx2007-iterations}
\end{figure}

@@

\section{Results}
\label{sec:results}
We evaluate the methods on held out data by using standardized mean square error (SMSE) of the test points with the predicted mean, and the negative log predictive density (NLPD) of the Gaussian likelihood of the inferred model. NLPD takes confidence into account, while SMSE only evaluates the mean prediction. In both cases, lower values represent better performance. We evaluated the performance of our flexible representations of the kernel, \textsc{sum}, \textsc{bt}, and \textsc{slfm}, by computing exact gradients using the standard Cholesky algorithm for a grid of different kernels (see Supplement).\footnote{Hyperparameters for the stopping condition, code, and benchmarking scripts are available in <anonymous repository>.}

@@

\begin{wrapfigure}{r}{0.5\textwidth}
%\begin{figure}[!h]
\centering
{\includegraphics[width=0.4\columnwidth]{m_time_nlpd.eps}}
\caption{Average and standard error of NLPD and runtime of the SLFM model on LLGP across over varying interpolating points. Every setting was run $10$ times.}
\label{fig:llgpweather}
%\end{figure}
\end{wrapfigure}

>>>>

\PassOptionsToPackage{numbers, compress}{natbib}
% Camera ready: \usepackage[final]{nips_2017}
\usepackage[final]{nips_2017}

@@

\begin{figure}[!h]
\begin{center}
  \subfigure[]{\includegraphics[width=0.4\columnwidth]{iterations.pdf}}
  \subfigure[]{\includegraphics[width=0.4\columnwidth]{running_cutoff.pdf}}
\end{center}
\caption{Trace of (a) the number of MVMs that \textsc{minres} must perform to invert $K_{|\bsth}^{-1}\Ty$ and (b) $\mcL, \norm{\nabla\mcL}$ given $\bsth$ at each optimization iteration for a GP applied to the dataset in Sec.~\ref{fx2007-results}. In (b), in green, we have 20\% of the rolling maximum $\infty$-norm of previous gradients.
}
\label{fx2007-iterations}
\end{figure}

@@

\section{Results}
\label{sec:results}
We evaluate the methods on held out data by using standardized mean square error (SMSE) of the test points with the predicted mean, and the negative log predictive density (NLPD) of the Gaussian likelihood of the inferred model. NLPD takes confidence into account, while SMSE only evaluates the mean prediction. In both cases, lower values represent better performance. We evaluated the performance of our flexible representations of the kernel, \textsc{sum}, \textsc{bt}, and \textsc{slfm}, by computing exact gradients using the standard Cholesky algorithm for a grid of different kernels (see Supplement).\footnote{Hyperparameters for the stopping condition, code, and benchmarking scripts are available in \url{https://github.com/vlad17/runlmc}.}

@@

\begin{wrapfigure}{r}{0.5\textwidth}
%\begin{figure}[!h]
\centering
{\includegraphics[width=0.4\columnwidth]{m_time_nlpd.pdf}}
\caption{Average and standard error of NLPD and runtime of the SLFM model on LLGP across over varying interpolating points. Every setting was run $10$ times.}
\label{fig:llgpweather}
%\end{figure}
\end{wrapfigure}
